Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational

### 2016-09-16 ms_pre_post.Rmd
Add small changes to Abstract

---
title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational approach"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

Inbreeding avoidance has been observed through pre-copulatory and post-copulatory mechanisms in empirical systems as a consequence of inbreeding depression. However, no models compare evolution of pre-copulatory versus post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of, and constraints on, inbreeding strategies. Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry. Accordingly, use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address four questions: (1) Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry? (2) Will selection for one costly inbreeding strategy be negligible given a non-costly complementary strategy? (3) Will constraints on evolution of one inbreeding strategy increase selection on an alternative strategy? And (4) will selection for one inbreeding strategy be negligible given existence of an already adaptive alternative strategy? We show that evolution of polyandry is greatly facilitated by evolution of post-copulatory inbreeding avoidance. Costs and constraints on pre-copulatory inbreeding avoidance generally affected evolution of post-copulatory inbreeding avoidance, but not vice versa. Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in empirical systems.

>>>>

---
title: 'Evolution of pre-copulatory and post-copulatory inbreeding behaviour: a computational
  approach'
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
csl: evolution.csl
bibliography: ms_pre_post.bib
---

@@

Inbreeding avoidance has been widely observed through pre-copulatory and post-copulatory mechanisms as a consequence of inbreeding depression in offspring viability. However, no models compare evolution of pre-copulatory and post-copulatory inbreeding avoidance jointly, and given biologically relevant costs of, and constraints on, inbreeding strategies. Critically, evolution of post-copulatory inbreeding avoidance is restricted to females that mate multiply, potentially leading to complex evolutionary dynamics among inbreeding strategies and polyandry. Accordingly, use individual-based modelling to track evolution of polyandry and inbreeding strategies under multiple costs and constraints to address four questions: (1) Will evolution of post-copulatory inbreeding avoidance strengthen selection for polyandry? (2) Will selection for one costly inbreeding strategy be negligible given a non-costly complementary strategy? (3) Will constraints on evolution of one inbreeding strategy increase selection on an alternative strategy? And (4) will selection for one inbreeding strategy be negligible given existence of an already adaptive alternative strategy? We show that evolution of polyandry is greatly facilitated by evolution of post-copulatory inbreeding avoidance. Costs and constraints on pre-copulatory inbreeding avoidance generally affected evolution of post-copulatory inbreeding avoidance, but not vice versa. Our model thereby introduces a novel framework for predicting evolution of both pre-copulatory and post-copulatory inbreeding strategies in empirical systems.
